A review of Crime data and how GDP affects Crime Rates

### 2017-03-08 paper/paper.Rmd
working on formatting

---
title: "Final Project Paper"
output:
  html_document: default
  html_notebook: default
---

>>>>

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ~/Dropbox/miscelanea/svm-r-markdown-templates/svm-latex-ms.tex
title: "A review of Crime data and how GDP affects Crime Rates"
author:
- name: Kai Yoshino
  affiliation: Univeristy of Washington
- name: Isabella Spaletta 
  affiliation: University of Washington
- name: Rembrandt Q. Einstein
  affiliation: Springfield University
abstract: "This document provides an introduction to R Markdown, argues for its..."
keywords: "pandoc, r markdown, knitr"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
# spacing: double
bibliography: ~/Dropbox/master.bib
biblio-style: apsr
---
